Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-09-10 ehp_revision/response_to_reviewers.Rmd

\medskip

\begin{shaded}
\textbf{R2 Comment 4:}
Table 2: This is another confusing table. Not sure what compared here. The
second column is a mean \# of exposed counties over years and the third column
seems like showing single storm with the max \# of exposed counties. Not sure
what info I should digest from this table.
\end{shaded}

**Response:**

We hope that these results can help epidemiologists who are planning new
single-storm or multi-year studies of tropical cyclones and associated health
risks. For planning a multi-year study, it is helpful to know how many exposures
the study might incorporate, as this can help in giving a general idea of
whether the study might have adequate statistical power to investigate a certain
research question. Similarly, for single-storm studies, it is helpful to know
how widespread exposure can be for a specific hazard during a very large storm.
This table provides some basic summaries of the extent of exposure to different
tropical cyclone hazards, both on average for the storms in the study and also
for those storms that were most extensive.

We have added text to help the readers interpret this table:

> **Text from Results of revised manuscript (added text in bold):**
"**Table 2 provides summary statistics describing the extent of counties
assessed as exposed based on specific storm hazards, to help epidemiologists in
planning studies, including understanding the potential statistical power to
study specific exposures, both for multi-storm and single-storm studies.**
Across the four storm hazards considered, there was wide variation in the
average number of county exposures per year. For tropical cyclone
tornadoes, there were on average about 40 county exposures per year within our
study. County exposures were more frequent for tropical cyclone wind exposures
(>160/year on average), even more frequent for tropical cyclone flood exposures
(>190/year on average), and most frequent for tropical cyclone rain exposure
(>290/year on average). For every hazard except tornadoes, we identified at
least one tropical cyclone that exposed over 250 counties (Table 2). However,
the largest-extent tropical cyclone varied across hazards: Frances in 2004
exposed the most counties based on rain, Michael in 2018 based on wind, and Ivan
in 2004 based on flooding and tornadoes (Table 2)."

### 2020-09-10 ehp_revision/writing/ehp_results.tex
Work some more on revisions

We used this storm exposure data to classify counties as exposed or unexposed
to four different hazards for each tropical cyclone and then explored patterns
over years with available data. Across the four storm hazards considered, there
was wide variation in the average number of county exposures per year
(Table~\ref{tab:exposuresummaries}). For tropical cyclone tornadoes,
there were on average about 40 county exposures per year within our study.
County exposures were more frequent for tropical cyclone wind exposures ($>$160
/ yr on average), even more frequent for tropical cyclone flood exposures
($>$190 / yr on average), and most frequent for tropical cyclone rain exposure
($>$290 / yr on average). For every hazard except tornadoes, we identified at
least one tropical cyclone that exposed over~250 counties
(Table~\ref{tab:exposuresummaries}).  However, the largest-extent tropical
cyclone varied across hazards: Frances in~2004 exposed the most counties based
on rain, Michael in~2018 based on wind, and Ivan in 2004 based on flooding and
tornadoes (Table~\ref{tab:exposuresummaries}).

>>>>

We used this storm exposure data to classify counties as exposed or unexposed
to four different hazards for each tropical cyclone and then explored patterns
over years with available data. \textbf{Table~\ref{tab:exposuresummaries}
provides summary statistics describing the extent of counties assessed as
exposed based on specific storm hazards, to help epidemiologists in planning
studies, including understanding the potential statistical power to study
specific exposures, both for multi-storm and single-storm studies.} Across the
four storm hazards considered, there was wide variation in the average number
of county exposures per year. For tropical cyclone tornadoes, there were on
average about 40 county exposures per year within our study.  County exposures
were more frequent for tropical cyclone wind exposures ($>$160 / yr on
average), even more frequent for tropical cyclone flood exposures ($>$190 / yr
on average), and most frequent for tropical cyclone rain exposure ($>$290 / yr
on average). For every hazard except tornadoes, we identified at least one
tropical cyclone that exposed over~250 counties
(Table~\ref{tab:exposuresummaries}).  However, the largest-extent tropical
cyclone varied across hazards: Frances in~2004 exposed the most counties based
on rain, Michael in~2018 based on wind, and Ivan in 2004 based on flooding and
tornadoes (Table~\ref{tab:exposuresummaries}).
